### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Update Abstract

[TK rewrite with region results]

Strong son preference is typically associated with shorter birth spacing
in the absence of sons, but access to sex selection has the potential to
reverse this pattern because each abortion extends spacing by six to
twelve months. 
I introduce a statistical method that simultaneously accounts for how sex selection 
increases both the spacing between births and the likelihood of a son. 
Using the four rounds of India's National Family and Health Surveys, I show that
the spacing between births increased substantially over the last four
decades, with the most substantial increases among women most 
likely to use sex selection.
Specifically, well-educated women with no boys now
exhibit significantly longer spacing and more male-biased sex ratios
than similar women with boys. 
Women with no education still follow the standard
pattern of short spacing when they have girls and little evidence of sex
selection, with medium-educated women showing mixed results.

\noindent JEL: J1, O12, I1
\noindent Keywords: India, prenatal sex determination, censoring, competing risk
\end{abstract}

>>>>

Strong son preference is typically associated with shorter birth spacing in the absence of 
sons, but access to sex selection has the potential to reverse this pattern because each 
abortion extends spacing by six to twelve months. 
I introduce an empirical method that simultaneously accounts for how sex selection 
increases both birth spacing and the likelihood of a son. 
Using the four rounds of India's National Family and Health Surveys, I show that birth 
intervals increased substantially over the last four decades, most substantially among 
women most likely to use sex selection.
Specifically, well-educated women with no boys now exhibit significantly longer spacing, 
and more male-biased sex ratios, than similar women with boys. 
Women with no education still follow the standard pattern of short average spacing when 
they have girls and little evidence of sex selection, with medium-educated women showing 
mixed results.
Furthermore, the traditional pattern of longer average spacing with sons appears to arise 
not from fewer very short birth intervals, but rather from the upper end of the distribution.
Finally, northern and western India are responsible for most of the spacing pattern 
reversal, although even the south experienced substantial increased intervals from
sex selection.

\noindent JEL: J1, O12, I1
\noindent Keywords: India, prenatal sex determination, censoring, competing risk, non-proportional hazard
\end{abstract}
